\LARGE How coexistence mechanisms mediate temporal stability

### 2016-02-19 manuscript/manuscript.Rmd
Update formula for resource uptake function as Hill function.
removew conceptual figure

```{r figure_1, dependson="plot-options", fig.cap="Diagram of our semi-discrete consumer-resource model. Solid lines show continuous dynamics while dashed lines show the discrete transitions.", cache=FALSE, results='hide', fig.width=4, fig.height=6}
library(png)
library(grid)
img <- readPNG("ConceptFig.png")
grid.raster(img)
```

@@

where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, and $m$s are biomass loss rates. The growth rate of living biomass is a resource-dependent function, $f_{i}(R) = r_{i}e^{-\alpha_{i}e^{-\beta_{i}R}}$. Resource depletion is equal to the sum of each species' consumption, $\sum_{i=1,2}f_{i}(R)N_{i}$. Note that since transitions between $N$ and $D$ are pulsed, only biomass loss occurs throughout the season for $D$.

@@

Following @Adler2008, we generated sequences of (un)correlated dormant-to-live state transition rates ($g$) for each species by drawing from multivariate normal distributions with mean 0 and a variance-covariance matrix of

\begin{align}
\begin{bmatrix}
\sigma^2_{E} & \rho\sigma^2_{E} \\
\rho\sigma^2_{E} & \sigma^2_{E}
\end{bmatrix}
\end{align}

>>>>

```{r figure_1, dependson="plot-options", fig.cap="Diagram of our semi-discrete consumer-resource model. Solid lines show continuous dynamics while dashed lines show the discrete transitions.", cache=FALSE, results='hide', fig.width=4, fig.height=6, eval=FALSE}
library(png)
library(grid)
img <- readPNG("ConceptFig.png")
grid.raster(img)
```

@@

where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, and $m$s are biomass loss rates. The growth rate of living biomass is a resource-dependent Hill function, $f_{i}(R) = r_{i}R^{\alpha_{i}} / (\beta_{i}^{\alpha_{i}}+R^{\alpha_{i}})$. Resource depletion is equal to the sum of each species' consumption, $\sum_{i=1,2}f_{i}(R)N_{i}$. Note that since transitions between $N$ and $D$ are pulsed, only biomass loss occurs throughout the season for $D$.

@@

Following @Adler2008, we generated sequences of (un)correlated dormant-to-live state transition rates ($g$) for each species by drawing from multivariate normal distributions with mean 0 and a variance-covariance matrix ($\Sigma_g$) of

\begin{align}
\Sigma_g = 
\begin{bmatrix}
\sigma^2_{E} & \rho\sigma^2_{E} \\
\rho\sigma^2_{E} & \sigma^2_{E}
\end{bmatrix}
\end{align}

### 2016-02-19 manuscript/manuscript.tex
Update formula for resource uptake function as Hill function.
removew conceptual figure

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

%%% Change title format to be more compact
\usepackage{titling}
\setlength{\droptitle}{-2em}
  \title{}
  \pretitle{\vspace{\droptitle}}
  \posttitle{}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Diagram of our semi-discrete consumer-resource model. Solid
lines show continuous dynamics while dashed lines show the discrete
transitions.}
\end{figure}

@@

where \(i\) denotes species, \(D\) is the dormant (long-lived) biomass
state, \(N\) is the living biomass (fast-growing, shorter-lived) state,
and \(m\)s are biomass loss rates. The growth rate of living biomass is
a resource-dependent function,
\(f_{i}(R) = r_{i}e^{-\alpha_{i}e^{-\beta_{i}R}}\). Resource depletion
is equal to the sum of each species' consumption,
\(\sum_{i=1,2}f(R)N_{i}\). Note that since transitions between \(N\) and
\(D\) are pulsed, only biomass loss occurs throughout the season for
\(D\).

@@

where \(D(T^-)\), \(N(T^-)\), and \(R(T^-)\) are the densities of each
state at the end of the year and \(g\) is a time-fluctuating activation
rate that regulates how much dormant biomass is converted to
growing-season live biomass each year. \(R(T^+)\) is a randomly
generated resource pulse. Our formulation assumes that at the end of
each season all accumulated living biomass {[}\(N(T^-)\){]} is converted
to dormant biomass.

@@

Following Adler and Drake (2008), we generated sequences of
(un)correlated dormant-to-live state transition rates (\(g\)) for each
species by drawing from multivariate normal distributions with mean 0
and a variance-covariance matrix of

\begin{align}
\begin{bmatrix}
\sigma^2_{E} & \rho\sigma^2_{E} \\
\rho\sigma^2_{E} & \sigma^2_{E}
\end{bmatrix}
\end{align}

@@

Some preliminary results from running simulations of the storage effect
version of the model at different levels of environmental cue
variability (\(\sigma_{E}\)) and resource supply variability
(\(\sigma_{S}\)). I ran 20 simulations at each combination of
\(\sigma_{E}\) and \(\sigma_{S}\) shown in
Figure\textasciitilde{}\ref{fig:storeEffSims} (the points are the means
across the 20 simulations, each run for 2,000 time-steps, with the
initial 1,000 time-steps discarded before calculating anything). There
is a weak trend of community CV to saturate at high levels of resource
supply variability (Figure\textasciitilde{}\ref{fig:storeEffSims}, top
panel).

One of the things we are interested in is how well the community buffers
itself against resource variability. Really I should calculate some kind
of asynchrony metric, but for now I just looked at the ratio of the
resource CV to the community CV
(Figure\textasciitilde{}\ref{fig:storeEffSims}, bottom panel). Kind of
difficult to interpret, but it is interesting that at high levels of
variability in the environmental cue that drives the storage effect, the
ratio decreases with resource supply variability. The opposite occurs at
lower levels of variability in the environmental cue.

@@

Adler, P. B., and J. M. Drake. 2008. Environmental variation, stochastic
extinction, and competitive coexistence. The American naturalist
172:186--195.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{}
  \pretitle{\vspace{\droptitle}}
  \posttitle{}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

@@

where \(i\) denotes species, \(D\) is the dormant (long-lived) biomass
state, \(N\) is the living biomass (fast-growing, shorter-lived) state,
and \(m\)s are biomass loss rates. The growth rate of living biomass is
a resource-dependent Hill function,
\(f_{i}(R) = r_{i}R^{\alpha_{i}} / (\beta_{i}^{\alpha_{i}}+R^{\alpha_{i}})\).
Resource depletion is equal to the sum of each species' consumption,
\(\sum_{i=1,2}f_{i}(R)N_{i}\). Note that since transitions between \(N\)
and \(D\) are pulsed, only biomass loss occurs throughout the season for
\(D\).

@@

where \(D(T^-)\), \(N(T^-)\), and \(R(T^-)\) are the densities of each
state at the end of the year and \(g\) is a time-fluctuating activation
rate that regulates how much dormant biomass is converted to
growing-season live biomass each year. \(R(T^+)\) is a randomly
generated resource pulse from a log-normal distribution with mean
\(\mu_{R}\) and standard deviation \(\sigma_{R}\). Our formulation
assumes that at the end of each season all accumulated living biomass
{[}\(N(T^-)\){]} is converted to dormant biomass.

@@

Following ({\textbf{???}}), we generated sequences of (un)correlated
dormant-to-live state transition rates (\(g\)) for each species by
drawing from multivariate normal distributions with mean 0 and a
variance-covariance matrix (\(\Sigma_g\)) of

\begin{align}
\Sigma_g = 
\begin{bmatrix}
\sigma^2_{E} & \rho\sigma^2_{E} \\
\rho\sigma^2_{E} & \sigma^2_{E}
\end{bmatrix}
\end{align}

@@

@@
